### 2019-11-06 report/paper.tex
Add section paragraph in introduction describing train and test data used (not yet finished)

\begin{itemize}
    \item 80 high resolution images from the \textit{Where's Waldo} book series
    \item 
    \item training a linear support vector machine (SVM) to create a multiclass-classifier
\end{itemize}

>>>>

The data we utilised can be summarised as follows:

\begin{itemize}
    \item 80 high resolution images from the \textit{Where's Waldo} book series
    \item 137 images of Waldo cropped to the patch of the image as describe in the annotation files
    \item 43 images of Wenda cropped to the patch of the image as describe in the annotation files
    \item 27 images of Wizard cropped to the patch of the image as describe in the annotation files
    \item Approximately 14,000 to 15,000 images (128x128px) subsampled from the original images, which did neither contain Waldo, Wenda or Wizard, used as negative training samples
\end{itemize}

In order to assess the performance of our algorithms we split the given set of images in a training and a testing set. This reduced the amount of positive samples of the three characters to 124 training samples for Waldo, 36 for Wenda and 24 for Wizard. As we will discuss in the upcoming sections, this uneaven split of training samples influenced the performance of our solution for the three different classes.
